---
title: 'TWS Workshop 2019: Getting Started'
author: "Avgar, Fieberg, Signer"
date: "September 20, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Steps to prepare for the workshop & to make sure your computer is ready to go!

1. Download latest versions of RStudio and R from here (**you should be working with R >= 3.5 and RStudio >= 1.2**):
    a. https://cloud.r-project.org/
    b. https://www.rstudio.com/
2. Download the data and materials for this workshop. There are two options here: 
    a. You can download the repository from https://github.com/jmsigner/workshop_2019_tws/archive/master.zip and unzip it to a known location on your computer.
    b. If you are familiar with working with git and github, you can simply clone the repository with: 
    
```
git clone git@github.com:jmsigner/workshop_2019_tws.git
```

3. Open Rstudio and create a project associated with this directory. `File -> New Project`, then select `Existing directory`, find the `workshop_tws_2019 directory` on your computer and click OK.
4. Install the following packages (with dependencies) by executing the following command: 

```{r, eval = FALSE}
install.packages(c("knitr", "lubridate", "sf", "raster", "move", "amt", 
                   "glmmTMB", "tidyverse", "tidyr"), dep = TRUE)
```

5. Open the script named `scripts/test_vignette.r`.  In RStudio, choose `File -> Knit Document`. Select `html` and click `Compile Document`. It took my computer 2.5 minutes to run everything (but, may take longer on your computer depending on its specs).  Please check over the resulting `html` file (`scripts/test_vignette.html`) and send a copy to bsmity13@gmail.com. If you encounter problems, please contact jsigner@gwdg.de. 
